\input{./._relpath-to-latexroot.ltx}
\documentclass[\latexroot/\projectname]{subfiles}
\input{\latexroot/@resources/subfile-setup.ltx}

\begin{document}

\FloatBarrier
\section{Comparing fiscal stimulus policies}
\whenintegrated{\label{sec:comparing}} % integrated doc: SST for labels

In this section, we present our results where we compare three policies to provide fiscal stimulus in our calibrated model. 

\subsection{Impulse responses}
\whenintegrated{\label{sec:IRFs}} % integrated doc: SST for labels

The impulse responses that we present for each stimulus policy are constructed as follows:
\begin{itemize}
  \setlength{\itemsep}{0.0ex}
  \item
        A recession hits in quarter one.
\end{itemize}

\subsubsection{Stimulus check}

Figure~\ref{fig:recessioncheckrelrecession} shows the impulse response of income and consumption when stimulus checks are issued in the first quarter of a recession.

\subsubsection{UI extension}

The impulse responses in Figure~\ref{fig:recessionuirelrecession} show the response to a policy that extends unemployment benefits from 6 months to 12 months for a period of a year.

\subsubsection{Payroll tax cut}

The final impulse response graph, Figure~\ref{fig:recessiontaxcutrelrecession}, shows the impulse response for a payroll tax cut that persists for two years (eight quarters).

\subsection{Multipliers}
\whenintegrated{\label{sec:multipliers}} % integrated doc: SST for labels

In this section, we compare the fiscal multipliers across the three stimulus policies.

\subsection{Welfare}
\whenintegrated{\label{sec:welfare}} % integrated doc: SST for labels

In this section, we look at the welfare implications of each stimulus policy.

\subfile{../Tables/welfare6}

Table~\ref{tab:welfare6} shows the welfare measure for each policy as defined by equation~\eqref{welfare6}.

\subsection{Comparing the policies}
\whenintegrated{\label{subsec:comparing-the-policies}} % integrated doc: SST for labels

The results presented in sections~\ref{sec:multipliers} and~\ref{sec:welfare} indicate that the extension of unemployment benefits is the clear ``bang for the buck'' winner.

\FloatBarrier
\subsection{Results in a model without the splurge}

We introduce the splurge in our model with the aim of matching empirical evidence on the dynamics of spending in response to transitory income shocks.

% Bibliography inclusion handled automatically by document structure
\smartbib

\end{document}
